Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-08-03 main-sketch.tex
fixed formula

This mechanism is based on the basic exponential mechanism
\cite{talwar}, with $\betaset$ as the range and
$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
that in this mechanism we don't calibrate the noise w.r.t. to the
global sensitivity of the scoring function but w.r.t. to the smooth
sensitivity $S(\dataobs)$ -- defined by \citet{nissim2007smooth}-- of
$\hellinger(\bysinfer(\dataobs), \cdot)$. The smooth sensitivity is
computed as follows:
\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(C(\dataobs), C(\dataobs'))}\bigg\},
\end{equation}
where $d$ is the $\frac{1}{2}\cdot \ell_1$ distance between two datasets,
$C$ takes a datasets and maps it to its histogram,
$\gamma =
\gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
be determined later, and where $\Delta_{l}\bigg
(\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$ denotes the local
sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
of the scoring function used in our mechanism. That is:
\begin{equation*}
\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert.
\end{equation*}

>>>>

This mechanism is based on the basic exponential mechanism
\cite{talwar}, with $\betaset$ as the range and
$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
that in this mechanism we don't calibrate the noise w.r.t. to the
global sensitivity of the scoring function but w.r.t. to the smooth
sensitivity $S(\dataobs)$ -- defined by \citet{nissim2007smooth}-- of
$\hellinger(\bysinfer(\dataobs), \cdot)$. The smooth sensitivity is
computed as follows:
\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(C(\dataobs), C(\dataobs'))}\bigg\},
\end{equation}
where $d$ is the $\frac{1}{2}\cdot \ell_1$ distance between two histograms,
$C$ takes a datasets and maps it to its histogram,
$\gamma =
\gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
be determined later, and where $\Delta_{l}\bigg
(\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$ denotes the local
sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
of the scoring function used in our mechanism. That is:
\begin{equation*}
\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert.
\end{equation*}
